Current Models

### 2019-10-30 models.Rmd
Update models.Rmd

## AutoARIMA

@@

>>>>

## AutoArima

@@

## NaiveArima

NaiveArima (Naive Auto-Regressive Integrated Moving Average) is a fixed
Auto-Regressive Integrated Moving Average (ARIMA) model of order (0,1,0) 
fit to the data at the composite (full site and just control plots) spatial
level and both the composite (community) and the articulated (species) 
ecological levels. The model is selected and fitted using the `Arima` 
and `forecast` functions in the **forecast** package 
[@Hyndman2013; @Hyndman2017] and the 
`NaiveArima` function in our 
[**portalcasting** package](https://github.com/weecology/portalcasting).
